ABM simulating short-term mating behaviors

### 2022-05-12 submission/manuscript.Rmd
added abstract, minor modification of the manuscript, close #17

@@

The model measured **three** outcomes: (1) the number of men and women who had ever engaged in short-term mating **put this to the end**; (2) the number of short-term mating experiences of men and women; (3) the number of short-term mates of men and women. The number of short-term mating experienced and short-term mates were calculated by taking the average among the whole men/women population and among those who had engaged in short-term mating.

@@

### Initial setup
In total, 150 women and 150 men were created on the lattice at random locations. All agents were initialized with (1) a three-unit maximum distance by which agents can move away from their birthplace (movement range); (2) a 10% likelihood of two agents forming a long-term relationship upon meeting; (3) single status and no long-term partner; (4) a mate value, sampled from a Gaussian distribution (*M* = 5, *SD* = 1.5); (5) no short-term mate or short-term mating history.

>>>>

Gender differences in short-term mating behaviors have been a well-documented phenomenon in human sexuality research. Existing studies usually conflate gender differences in preferences for short-term mating with differences in sexual behaviors, which is theoretically dubious. Using an agent-based model, the present study investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances. The results suggested that heterosexual men and women had the same average number of short-term mating experiences and short-term mates even when gender differences in preferences fort-term mating existed. Gender differences in mating behaviors only emerged when heterosexual men and women in the mating pool were considered. Moreover, gay men had a higher average number of both outcomes than lesbian women and than heterosexual men under such a circumstance. These results suggest that theoretically speaking, gender differences in short-term mating behaviors only occurred among particular populations, or when men's preferences for short-term mating are not constrained by those of women. Suggestions for future research in human mating psychology and behaviors were provided.

\

*Keywords:* agent-based modeling, short-term mating, casual sex, sexual strategy theory, female choice hypothesis

@@

The model measured two outcomes: (1) the number of short-term mating experiences of men and women; (2) the number of short-term mates of men and women. Additionally, we had also documented the number of men and women in the mating pool (i.e., who had ever engaged in short-term mating); The average number of short-term mating experiences and short-term mates were calculated by taking the average among the whole population of men/women (*N~m~* = *N~w~* = 150) and among those who had engaged in short-term mating.

@@

### Initial setup
In total, 150 women and 150 men were created on the lattice at random locations. All agents were initialized with (1) a three-unit maximum distance by which agents can move away from their birthplace (movement range); (2) a 10% likelihood of two agents forming a long-term relationship upon meeting; (3) single status and no long-term partner; (4) a mate value, sampled from a Gaussian distribution (*M* = 5.0, *SD* = 1.5); (5) no short-term mate or short-term mating history.

### 2022-05-12 submission/manuscript.tex
added abstract, minor modification of the manuscript, close #17

@@

The model measured \textbf{three} outcomes: (1) the number of men and
women who had ever engaged in short-term mating \textbf{put this to the
end}; (2) the number of short-term mating experiences of men and women;
(3) the number of short-term mates of men and women. The number of
short-term mating experienced and short-term mates were calculated by
taking the average among the whole men/women population and among those
who had engaged in short-term mating.

@@

In total, 150 women and 150 men were created on the lattice at random
locations. All agents were initialized with (1) a three-unit maximum
distance by which agents can move away from their birthplace (movement
range); (2) a 10\% likelihood of two agents forming a long-term
relationship upon meeting; (3) single status and no long-term partner;
(4) a mate value, sampled from a Gaussian distribution (\emph{M} = 5,
\emph{SD} = 1.5); (5) no short-term mate or short-term mating history.

>>>>

Gender differences in short-term mating behaviors have been a
well-documented phenomenon in human sexuality research. Existing studies
usually conflate gender differences in preferences for short-term mating
with differences in sexual behaviors, which is theoretically dubious.
Using an agent-based model, the present study investigated whether men
and women's different mating preferences resulted in any gender
differences in short-term mating behaviors, and if they did, under what
circumstances. The results suggested that heterosexual men and women had
the same average number of short-term mating experiences and short-term
mates even when gender differences in preferences fort-term mating
existed. Gender differences in mating behaviors only emerged when
heterosexual men and women in the mating pool were considered. Moreover,
gay men had a higher average number of both outcomes than lesbian women
and than heterosexual men under such a circumstance. These results
suggest that theoretically speaking, gender differences in short-term
mating behaviors only occurred among particular populations, or when
men's preferences for short-term mating are not constrained by those of
women. Suggestions for future research in human mating psychology and
behaviors were provided.

~

\emph{Keywords:} agent-based modeling, short-term mating, casual sex,
sexual strategy theory, female choice hypothesis

@@

The model measured two outcomes: (1) the number of short-term mating
experiences of men and women; (2) the number of short-term mates of men
and women. Additionally, we had also documented the number of men and
women in the mating pool (i.e., who had ever engaged in short-term
mating); The average number of short-term mating experiences and
short-term mates were calculated by taking the average among the whole
population of men/women (\emph{N\textsubscript{m}} =
\emph{N\textsubscript{w}} = 150) and among those who had engaged in
short-term mating.

@@

In total, 150 women and 150 men were created on the lattice at random
locations. All agents were initialized with (1) a three-unit maximum
distance by which agents can move away from their birthplace (movement
range); (2) a 10\% likelihood of two agents forming a long-term
relationship upon meeting; (3) single status and no long-term partner;
(4) a mate value, sampled from a Gaussian distribution (\emph{M} = 5.0,
\emph{SD} = 1.5); (5) no short-term mate or short-term mating history.
